---
title: "CDR3 comparison"
author: "Nils Eling"
output: 
  html_document:
    toc: true
    toc_depth: 2
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, 
        encoding = encoding, output_file = '/Users/nils/Dropbox (Cambridge University)/GammaDelta/Analysis/Clones/CDR3_comparison.html') })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This script studies the similarities of clone composition between different samples.

## Read in data

```{r}
library(plyr)
library(reshape2)
library(ggplot2)
library(cowplot)
library(pheatmap)
library(readxl)
source("../../Functions/auxiliary.R")

# Read in mixcr mapping results - one chain per .txt file
all.files <- list.files("/Users/nils/Dropbox (Cambridge University)/GammaDelta/Analysis/Clones/Txt_files", full.names = TRUE)

# Read in normalized counts
norm <- read.table("/Users/nils/Dropbox (Cambridge University)/GammaDelta/Analysis/Data/NormCounts.txt", sep = "\t", header = TRUE)
libraries <- sapply(colnames(norm), function(n){unlist(strsplit(n, "_"))[4]})

# Remove low quality libraries
all.files <- grep(paste(libraries,collapse="|"), all.files, value=TRUE, ignore.case = TRUE)

# All files containing TRG
TRG.files <- all.files[grepl("TRG", all.files)]
TRD.files <- all.files[grepl("TRD", all.files)]

# Chain annotation
annot <- as.data.frame(read_xls("/Users/nils/Dropbox (Cambridge University)/GammaDelta/Analysis/Clones/Variable_sequences_to_edit.xls"))
annot$`IMGT sub-group`[is.na(annot$`IMGT sub-group`)] <- annot$names[is.na(annot$`IMGT sub-group`)]
rownames(annot) <- annot$names
```

# TRG

## Collect top 10 expanded clones for each old library

```{r}
# Find clones - old
Vg1_old_TRG_V1 <- topCDR3(all.files, top = 10, keywords = c("Vg1", "old", "TRG"), select = "TCRG-V1")
#Vg1_old_TRG_V3 <- topCDR3(all.files, top = 10, keywords = c("Vg1", "old", "TRG"), select = "TCRG-V3")
Vg4_Th1_old_TRG_V4 <- topCDR3(all.files, top = 10, keywords = c("Vg4", "old", "TRG", "Th1-"), select = "TCRG-V4")
Vg4_Th17_old_TRG_V4 <- topCDR3(all.files, top = 10, keywords = c("Vg4", "old", "TRG", "Th17-"), select = "TCRG-V4")
Vg6_old_TRG_V6 <- topCDR3(all.files, top = 10, keywords = c("Vg6", "old", "TRG"), select = "TCRG-V6")

# Find clones - young
Vg1_young_TRG_V1 <- topCDR3(all.files, top = 10, keywords = c("Vg1", "young", "TRG"), select = "TCRG-V1")
#Vg1_young_TRG_V3 <- topCDR3(all.files, top = 10, keywords = c("Vg1", "young", "TRG"), select = "TCRG-V3")
Vg4_Th1_young_TRG_V4 <- topCDR3(all.files, top = 10, keywords = c("Vg4", "young", "TRG", "Th1-"), select = "TCRG-V4")
Vg4_Th17_young_TRG_V4 <- topCDR3(all.files, top = 10, keywords = c("Vg4", "young", "TRG", "Th17-"), select = "TCRG-V4")
Vg6_young_TRG_V6 <- topCDR3(all.files, top = 10, keywords = c("Vg6", "young", "TRG"), select = "TCRG-V6")
```

## Visuailze Vg1 cells

```{r}
# Merge clones
cur_clones <- data.frame(na = unique(c(Vg1_old_TRG_V1$na, Vg1_young_TRG_V1$na)),
                         aa = c(Vg1_old_TRG_V1$aa, Vg1_young_TRG_V1$aa)[
                           match(unique(c(Vg1_old_TRG_V1$na, Vg1_young_TRG_V1$na)),
                                 c(Vg1_old_TRG_V1$na, Vg1_young_TRG_V1$na))
                         ],
                         chain = c(Vg1_old_TRG_V1$chain, Vg1_young_TRG_V1$chain)[
                           match(unique(c(Vg1_old_TRG_V1$na, Vg1_young_TRG_V1$na)),
                                 c(Vg1_old_TRG_V1$na, Vg1_young_TRG_V1$na))
                         ])
rownames(cur_clones) <- cur_clones$na

c.names <- c(paste("Vg1_Th1-_old_TRG_V1", 
                   1:sum(grepl("Vg1_Th1-old", TRG.files)), 
                   sep =  "_"), 
                   paste("Vg1_Th1-_young_TRG_V1", 
                   1:sum(grepl("Vg1_Th1-young", TRG.files)), 
                   sep =  "_"))
cur_mat <- matrix(data = NA, ncol = length(c.names), 
              nrow = nrow(cur_clones))
colnames(cur_mat) <- c.names
rownames(cur_mat) <- cur_clones$na

for(i in c.names){
  cur_mat[,i] <- clones.fraction(all.files, i, cur_clones$na)
}
cur_mat <- cur_mat[order(rowMeans(cur_mat), decreasing = TRUE),]
rownames(cur_mat) <- paste(cur_clones[rownames(cur_mat),"na"],
                           cur_clones[rownames(cur_mat),"aa"], sep = ", ")

# Generate annotation data.frame
annot.df <- data.frame(row.names = rownames(cur_mat),
                       chain = cur_clones[sub(", [A-Z]*$", "", 
                                              rownames(cur_mat)),
                                          "chain"])

# Find old specific clones
cur_mat.old <- cur_mat[rowSums(cur_mat[,grepl("young", colnames(cur_mat))]) < 0.0001,]
cur_mat.old <- cur_mat.old[order(rowMeans(cur_mat.old), decreasing = TRUE),]

# Find young specific clones
cur_mat.young <- cur_mat[rowSums(cur_mat[,grepl("old", colnames(cur_mat))]) < 0.0001,]
cur_mat.young <- cur_mat.young[order(rowMeans(cur_mat.young), decreasing = TRUE),]

# Find shared clones
cur_mat.shared <- cur_mat[!(rownames(cur_mat) %in% 
                               c(rownames(cur_mat.old),
                                 rownames(cur_mat.young))),]
cur_mat.shared <- cur_mat.shared[order(rowMeans(cur_mat.shared), 
                                       decreasing = TRUE),]

# Visualize in form of heatmap
pdf("/Users/nils/Dropbox (Cambridge University)/GammaDelta/Analysis/Figures/Vg1_TRG_CDR3.pdf", 
    onefile = FALSE, width = 10, height = 10)
print(pheatmap(rbind(cur_mat.old, cur_mat.shared, cur_mat.young), 
         color = c("grey", colorRampPalette(c("white", "blue", "red"))(9999)),
         cluster_cols = FALSE, cluster_rows = FALSE, 
         breaks = seq(0, max(cur_mat), length.out = 10000), cellheight = 8, 
         fontsize = 7, gaps_row = c(nrow(cur_mat.old),
                                    nrow(cur_mat.old)+nrow(cur_mat.shared)),
         annotation_row = annot.df))
dev.off()
```

## Visuailze Vg4 cells

```{r}
# Merge clones
cur_clones <- data.frame(na = unique(c(Vg4_Th1_old_TRG_V4$na,
                                       Vg4_Th1_young_TRG_V4$na,
                                       Vg4_Th17_old_TRG_V4$na,
                                       Vg4_Th17_young_TRG_V4$na)),
                         aa = c(Vg4_Th1_old_TRG_V4$aa,
                                Vg4_Th1_young_TRG_V4$aa,
                                Vg4_Th17_old_TRG_V4$aa,
                                Vg4_Th17_young_TRG_V4$aa)[
                           match(unique(c(Vg4_Th1_old_TRG_V4$na,
                                       Vg4_Th1_young_TRG_V4$na,
                                       Vg4_Th17_old_TRG_V4$na,
                                       Vg4_Th17_young_TRG_V4$na)),
                                 c(Vg4_Th1_old_TRG_V4$na,
                                       Vg4_Th1_young_TRG_V4$na,
                                       Vg4_Th17_old_TRG_V4$na,
                                       Vg4_Th17_young_TRG_V4$na))
                         ],
                         chain = c(Vg4_Th1_old_TRG_V4$chain,
                                Vg4_Th1_young_TRG_V4$chain,
                                Vg4_Th17_old_TRG_V4$chain,
                                Vg4_Th17_young_TRG_V4$chain)[
                           match(unique(c(Vg4_Th1_old_TRG_V4$na,
                                       Vg4_Th1_young_TRG_V4$na,
                                       Vg4_Th17_old_TRG_V4$na,
                                       Vg4_Th17_young_TRG_V4$na)),
                                 c(Vg4_Th1_old_TRG_V4$na,
                                       Vg4_Th1_young_TRG_V4$na,
                                       Vg4_Th17_old_TRG_V4$na,
                                       Vg4_Th17_young_TRG_V4$na))
                         ])
rownames(cur_clones) <- cur_clones$na

c.names <- c(paste("Vg4_Th1-_young_TRG_V4", 
                   1:sum(grepl("Vg4_Th1-young", TRG.files)), 
                   sep =  "_"),
             paste("Vg4_Th1-_old_TRG_V4", 
                   1:sum(grepl("Vg4_Th1-old", TRG.files)), 
                   sep =  "_"), 
             paste("Vg4_Th17-_young_TRG_V4", 
                   1:sum(grepl("Vg4_Th17-young", TRG.files)), 
                   sep =  "_"),
             paste("Vg4_Th17-_old_TRG_V4", 
                   1:sum(grepl("Vg4_Th17-old", TRG.files)), 
                   sep =  "_"))
cur_mat <- matrix(data = NA, ncol = length(c.names), 
              nrow = nrow(cur_clones))
colnames(cur_mat) <- c.names
rownames(cur_mat) <- cur_clones$na

for(i in c.names){
  cur_mat[,i] <- clones.fraction(all.files, i, cur_clones$na)
}
cur_mat <- cur_mat[order(rowMeans(cur_mat), decreasing = TRUE),]
rownames(cur_mat) <- paste(cur_clones[rownames(cur_mat),"na"],
                           cur_clones[rownames(cur_mat),"aa"], sep = ", ")

# Generate annotation data.frame
annot.df <- data.frame(row.names = rownames(cur_mat),
                       chain = cur_clones[sub(", [A-Z]*$", "", 
                                              rownames(cur_mat)),
                                          "chain"])

# Find Th1 young specific clones
cur_mat.young.Th1 <- cur_mat[rowSums(cur_mat[,grepl("Th1-_old", 
                              colnames(cur_mat))]) < 0.0001 &
                               rowSums(cur_mat[,grepl("Th17-_young", 
                              colnames(cur_mat))]) < 0.0001 &
                               rowSums(cur_mat[,grepl("Th17-_old", 
                              colnames(cur_mat))]) < 0.0001,]
cur_mat.young.Th1 <- cur_mat.young.Th1[order(rowMeans(cur_mat.young.Th1),
                                             decreasing = TRUE),]

# Find Th1 old specific clones
cur_mat.old.Th1 <- cur_mat[rowSums(cur_mat[,grepl("Th1-_young", 
                                    colnames(cur_mat))]) < 0.0001 &
                             rowSums(cur_mat[,grepl("Th17-_old", 
                                    colnames(cur_mat))]) < 0.0001 &
                             rowSums(cur_mat[,grepl("Th17-_young", 
                                    colnames(cur_mat))]) < 0.0001,]
cur_mat.old.Th1 <- cur_mat.old.Th1[order(rowMeans(cur_mat.old.Th1), 
                                         decreasing = TRUE),]

# Find Th17 young specific clones
cur_mat.young.Th17 <- cur_mat[rowSums(cur_mat[,grepl("Th17-_old", 
                              colnames(cur_mat))]) < 0.0001 &
                                rowSums(cur_mat[,grepl("Th1-_young", 
                              colnames(cur_mat))]) < 0.0001 & 
                                rowSums(cur_mat[,grepl("Th1-_old", 
                              colnames(cur_mat))]) < 0.0001,]
cur_mat.young.Th17 <- cur_mat.young.Th17[order(rowMeans(cur_mat.young.Th17),
                                             decreasing = TRUE),]

# Find Th17 old specific clones
cur_mat.old.Th17 <- cur_mat[rowSums(cur_mat[,grepl("Th17-_young",
                                    colnames(cur_mat))]) < 0.0001 & 
                              rowSums(cur_mat[,grepl("Th1-_old", 
                                    colnames(cur_mat))]) < 0.0001 &
                              rowSums(cur_mat[,grepl("Th1-_young",
                                    colnames(cur_mat))]) < 0.0001,]
cur_mat.old.Th17 <- cur_mat.old.Th17[order(rowMeans(cur_mat.old.Th17), 
                                         decreasing = TRUE),]

# Find Th17  specific clones
cur_mat.Th17 <- cur_mat[rowSums(cur_mat[,grepl("Th17-_young", 
                              colnames(cur_mat))]) > 0.0001 &
                          rowSums(cur_mat[,grepl("Th17-_old", 
                              colnames(cur_mat))]) > 0.0001 &
                          rowSums(cur_mat[,grepl("Th1-_young", 
                              colnames(cur_mat))]) < 0.0001 &
                          rowSums(cur_mat[,grepl("Th1-_young", 
                              colnames(cur_mat))]) < 0.0001,]
cur_mat.Th17 <- cur_mat.Th17[order(rowMeans(cur_mat.Th17),
                                             decreasing = TRUE),]

# Find Th1  specific clones
cur_mat.Th1 <- cur_mat[rowSums(cur_mat[,grepl("Th1-_young", 
                              colnames(cur_mat))]) > 0.0001 &
                          rowSums(cur_mat[,grepl("Th1-_old", 
                              colnames(cur_mat))]) > 0.0001 &
                          rowSums(cur_mat[,grepl("Th17-_young", 
                              colnames(cur_mat))]) < 0.0001 &
                          rowSums(cur_mat[,grepl("Th17-_old", 
                              colnames(cur_mat))]) < 0.0001,]
cur_mat.Th1 <- cur_mat.Th1[order(rowMeans(cur_mat.Th1),
                                             decreasing = TRUE),]

# Find shared clones
cur_mat.shared <- cur_mat[!(rownames(cur_mat) %in% 
                               c(rownames(cur_mat.old.Th1),
                                 rownames(cur_mat.young.Th1),
                                 rownames(cur_mat.old.Th17),
                                 rownames(cur_mat.young.Th17),
                                 rownames(cur_mat.Th1),
                                 rownames(cur_mat.Th17))),]
cur_mat.shared <- cur_mat.shared[order(rowMeans(cur_mat.shared), 
                                       decreasing = TRUE),]

# Visualize in form of heatmap
pdf("/Users/nils/Dropbox (Cambridge University)/GammaDelta/Analysis/Figures/Vg4_TRG_CDR3.pdf", 
    onefile = FALSE, width = 10, height = 10)
print(pheatmap(rbind(cur_mat.young.Th1, cur_mat.old.Th1, cur_mat.Th1,
               cur_mat.shared, cur_mat.Th17, cur_mat.young.Th17,
               cur_mat.old.Th17), 
         color = c("grey", colorRampPalette(c("white", "blue", "red"))(9999)),
         cluster_cols = FALSE, cluster_rows = FALSE, 
         breaks = seq(0, max(cur_mat), length.out = 10000), cellheight = 8, 
         fontsize = 7, gaps_row = c(3, 8, 12, 54, 57, 65),
         annotation_row = annot.df))
dev.off()
```

## Visuailze Vg6 cells

```{r}
# Merge clones
cur_clones <- data.frame(na = unique(c(Vg6_old_TRG_V6$na, Vg6_young_TRG_V6$na)),
                         aa = c(Vg6_old_TRG_V6$aa, Vg6_young_TRG_V6$aa)[
                           match(unique(c(Vg6_old_TRG_V6$na, Vg6_young_TRG_V6$na)),
                                 c(Vg6_old_TRG_V6$na, Vg6_young_TRG_V6$na))
                         ],
                         chain = c(Vg6_old_TRG_V6$chain, Vg6_young_TRG_V6$chain)[
                           match(unique(c(Vg6_old_TRG_V6$na, Vg6_young_TRG_V6$na)),
                                 c(Vg6_old_TRG_V6$na, Vg6_young_TRG_V6$na))
                         ])
rownames(cur_clones) <- cur_clones$na

c.names <- c(paste("Vg6_Th17-_young_TRG_V6", 
                   1:sum(grepl("Vg6_Th17-young", TRG.files)), 
                   sep =  "_"), 
                   paste("Vg6_Th17-_old_TRG_V6", 
                   1:sum(grepl("Vg6_Th17-old", TRG.files)), 
                   sep =  "_"))
cur_mat <- matrix(data = NA, ncol = length(c.names), 
              nrow = nrow(cur_clones))
colnames(cur_mat) <- c.names
rownames(cur_mat) <- cur_clones$na

for(i in c.names){
  cur_mat[,i] <- clones.fraction(all.files, i, cur_clones$na)
}
cur_mat <- cur_mat[order(rowMeans(cur_mat), decreasing = TRUE),]
rownames(cur_mat) <- paste(cur_clones[rownames(cur_mat),"na"],
                           cur_clones[rownames(cur_mat),"aa"], sep = ", ")

# Generate annotation data.frame
annot.df <- data.frame(row.names = rownames(cur_mat),
                       chain = cur_clones[sub(", [A-Z]*$", "", 
                                              rownames(cur_mat)),
                                          "chain"])

# Find old specific clones
cur_mat.old <- cur_mat[rowSums(cur_mat[,grepl("young", colnames(cur_mat))]) < 0.0001,]
cur_mat.old <- cur_mat.old[order(rowMeans(cur_mat.old), decreasing = TRUE),]

# Find young specific clones
cur_mat.young <- cur_mat[rowSums(cur_mat[,grepl("old", colnames(cur_mat))]) < 0.0001,]
cur_mat.young <- cur_mat.young[order(rowMeans(cur_mat.young), decreasing = TRUE),]

# Find shared clones
cur_mat.shared <- cur_mat[!(rownames(cur_mat) %in% 
                               c(rownames(cur_mat.old),
                                 rownames(cur_mat.young))),]


# Visualize in form of heatmap
pdf("/Users/nils/Dropbox (Cambridge University)/GammaDelta/Analysis/Figures/Vg6_TRG_CDR3.pdf", 
    onefile = FALSE, width = 10, height = 10)
print(pheatmap(rbind(cur_mat.old, cur_mat.shared, cur_mat.young), 
         color = c("grey", colorRampPalette(c("white", "blue", "red"))(9999)),
         cluster_cols = FALSE, cluster_rows = FALSE, 
         breaks = seq(0, max(cur_mat), length.out = 10000), cellheight = 8, 
         fontsize = 7, gaps_row = c(nrow(cur_mat.old), nrow(cur_mat.old)+nrow(cur_mat.shared)),
         annotation_row = annot.df))
dev.off()
```

# TRD

## Collect top 10 expanded clones for each old library

```{r}
# Find clones - old
Vg1_old_TRD <- topCDR3(all.files, top = 10, keywords = c("Vg1", "old", "TRD"),
                       annotation = data.frame(row.names = rownames(annot),
                                               annotation = annot[,"IMGT sub-group"]))
Vg4_Th1_old_TRD <- topCDR3(all.files, top = 10, keywords = c("Vg4", "old", "TRD", "Th1-"),
                       annotation = data.frame(row.names = rownames(annot),
                                               annotation = annot[,"IMGT sub-group"]))
Vg4_Th17_old_TRD <- topCDR3(all.files, top = 10, keywords = c("Vg4", "old", "TRD", "Th17-"),
                       annotation = data.frame(row.names = rownames(annot),
                                               annotation = annot[,"IMGT sub-group"]))
Vg6_old_TRD <- topCDR3(all.files, top = 10, keywords = c("Vg6", "old", "TRD"),
                       annotation = data.frame(row.names = rownames(annot),
                                               annotation = annot[,"IMGT sub-group"]))

# Find clones - young
Vg1_young_TRD <- topCDR3(all.files, top = 10, keywords = c("Vg1", "young", "TRD"),
                       annotation = data.frame(row.names = rownames(annot),
                                               annotation = annot[,"IMGT sub-group"]))
Vg4_Th1_young_TRD <- topCDR3(all.files, top = 10, keywords = c("Vg4", "young", "TRD", "Th1-"),
                       annotation = data.frame(row.names = rownames(annot),
                                               annotation = annot[,"IMGT sub-group"]))
Vg4_Th17_young_TRD <- topCDR3(all.files, top = 10, keywords = c("Vg4", "young", "TRD", "Th17-"),
                       annotation = data.frame(row.names = rownames(annot),
                                               annotation = annot[,"IMGT sub-group"]))
Vg6_young_TRD <- topCDR3(all.files, top = 10, keywords = c("Vg6", "young", "TRD"),
                       annotation = data.frame(row.names = rownames(annot),
                                               annotation = annot[,"IMGT sub-group"]))
```

## Visuailze Vg1 cells

```{r}
# Merge clones
cur_clones <- data.frame(na = unique(c(Vg1_old_TRD$na, Vg1_young_TRD$na)),
                         aa = c(Vg1_old_TRD$aa, Vg1_young_TRD$aa)[
                           match(unique(c(Vg1_old_TRD$na, Vg1_young_TRD$na)),
                                 c(Vg1_old_TRD$na, Vg1_young_TRD$na))
                         ],
                         chain = c(Vg1_old_TRD$chain, Vg1_young_TRD$chain)[
                           match(unique(c(Vg1_old_TRD$na, Vg1_young_TRD$na)),
                                 c(Vg1_old_TRD$na, Vg1_young_TRD$na))
                         ],
                         stringsAsFactors = FALSE)
rownames(cur_clones) <- cur_clones$na

c.names <- c(paste("Vg1_Th1-_old_TRD_X", 
                   1:sum(grepl("Vg1_Th1-old", TRD.files)), 
                   sep =  "_"), 
                   paste("Vg1_Th1-_young_TRD_X", 
                   1:sum(grepl("Vg1_Th1-young", TRD.files)), 
                   sep =  "_"))
cur_mat <- matrix(data = NA, ncol = length(c.names), 
              nrow = nrow(cur_clones))
colnames(cur_mat) <- c.names
rownames(cur_mat) <- cur_clones$na

for(i in c.names){
  cur_mat[,i] <- clones.fraction(all.files, i, cur_clones$na)
}
cur_mat <- cur_mat[order(rowMeans(cur_mat), decreasing = TRUE),]
rownames(cur_mat) <- paste(cur_clones[rownames(cur_mat),"na"],
                           cur_clones[rownames(cur_mat),"aa"], sep = ", ")

# Generate annotation data.frame
annot.df <- data.frame(row.names = rownames(cur_mat),
                       chain = cur_clones[sub(", [A-Z]*$", "", 
                                              rownames(cur_mat)),
                                          "chain"])

# Find old specific clones
cur_mat.old <- cur_mat[rowSums(cur_mat[,grepl("young", colnames(cur_mat))]) < 0.0001,]
cur_mat.old <- cur_mat.old[order(rowMeans(cur_mat.old), decreasing = TRUE),]

# Find young specific clones
cur_mat.young <- cur_mat[rowSums(cur_mat[,grepl("old", colnames(cur_mat))]) < 0.0001,]
cur_mat.young <- cur_mat.young[order(rowMeans(cur_mat.young), decreasing = TRUE),]

# Find shared clones
cur_mat.shared <- cur_mat[!(rownames(cur_mat) %in% 
                               c(rownames(cur_mat.old),
                                 rownames(cur_mat.young))),]
cur_mat.shared <- cur_mat.shared[order(rowMeans(cur_mat.shared), 
                                       decreasing = TRUE),]

# Visualize in form of heatmap
pdf("/Users/nils/Dropbox (Cambridge University)/GammaDelta/Analysis/Figures/Vg1_TRD_CDR3.pdf", 
    onefile = FALSE, width = 10, height = 15)
print(pheatmap(rbind(cur_mat.old, cur_mat.shared, cur_mat.young), 
         color = c("grey", colorRampPalette(c("white", "blue", "red"))(9999)),
         cluster_cols = FALSE, cluster_rows = FALSE, 
         breaks = seq(0, max(cur_mat), length.out = 10000), cellheight = 8, 
         fontsize = 7, gaps_row = c(nrow(cur_mat.old), nrow(cur_mat.old)+nrow(cur_mat.shared)),
         annotation_row = annot.df))
dev.off()
```

## Visuailze Vg4 cells

```{r}
# Merge clones
cur_clones <- data.frame(na = unique(c(Vg4_Th1_old_TRD$na,
                                       Vg4_Th1_young_TRD$na,
                                       Vg4_Th17_old_TRD$na,
                                       Vg4_Th17_young_TRD$na)),
                         aa = c(Vg4_Th1_old_TRD$aa,
                                Vg4_Th1_young_TRD$aa,
                                Vg4_Th17_old_TRD$aa,
                                Vg4_Th17_young_TRD$aa)[
                           match(unique(c(Vg4_Th1_old_TRD$na,
                                       Vg4_Th1_young_TRD$na,
                                       Vg4_Th17_old_TRD$na,
                                       Vg4_Th17_young_TRD$na)),
                                 c(Vg4_Th1_old_TRD$na,
                                       Vg4_Th1_young_TRD$na,
                                       Vg4_Th17_old_TRD$na,
                                       Vg4_Th17_young_TRD$na))
                         ],
                         chain = c(Vg4_Th1_old_TRD$chain,
                                Vg4_Th1_young_TRD$chain,
                                Vg4_Th17_old_TRD$chain,
                                Vg4_Th17_young_TRD$chain)[
                           match(unique(c(Vg4_Th1_old_TRD$na,
                                       Vg4_Th1_young_TRD$na,
                                       Vg4_Th17_old_TRD$na,
                                       Vg4_Th17_young_TRD$na)),
                                 c(Vg4_Th1_old_TRD$na,
                                       Vg4_Th1_young_TRD$na,
                                       Vg4_Th17_old_TRD$na,
                                       Vg4_Th17_young_TRD$na))
                         ])
rownames(cur_clones) <- cur_clones$na

c.names <- c(paste("Vg4_Th1-_young_TRD_X", 
                   1:sum(grepl("Vg4_Th1-young", TRD.files)), 
                   sep =  "_"),
             paste("Vg4_Th1-_old_TRD_X", 
                   1:sum(grepl("Vg4_Th1-old", TRD.files)), 
                   sep =  "_"), 
             paste("Vg4_Th17-_young_TRD_X", 
                   1:sum(grepl("Vg4_Th17-young", TRD.files)), 
                   sep =  "_"),
             paste("Vg4_Th17-_old_TRD_X", 
                   1:sum(grepl("Vg4_Th17-old", TRD.files)), 
                   sep =  "_"))
cur_mat <- matrix(data = NA, ncol = length(c.names), 
              nrow = nrow(cur_clones))
colnames(cur_mat) <- c.names
rownames(cur_mat) <- cur_clones$na

for(i in c.names){
  cur_mat[,i] <- clones.fraction(all.files, i, cur_clones$na)
}
cur_mat <- cur_mat[order(rowMeans(cur_mat), decreasing = TRUE),]
rownames(cur_mat) <- paste(cur_clones[rownames(cur_mat),"na"],
                           cur_clones[rownames(cur_mat),"aa"], sep = ", ")

# Generate annotation data.frame
annot.df <- data.frame(row.names = rownames(cur_mat),
                       chain = cur_clones[sub(", [A-Z]*$", "", 
                                              rownames(cur_mat)),
                                          "chain"])

# Find Th1 young specific clones
cur_mat.young.Th1 <- cur_mat[rowSums(cur_mat[,grepl("Th1-_old", 
                              colnames(cur_mat))]) < 0.0001 &
                               rowSums(cur_mat[,grepl("Th17-_young", 
                              colnames(cur_mat))]) < 0.0001 &
                               rowSums(cur_mat[,grepl("Th17-_old", 
                              colnames(cur_mat))]) < 0.0001,]
cur_mat.young.Th1 <- cur_mat.young.Th1[order(rowMeans(cur_mat.young.Th1),
                                             decreasing = TRUE),]

# Find Th1 old specific clones
cur_mat.old.Th1 <- cur_mat[rowSums(cur_mat[,grepl("Th1-_young", 
                                    colnames(cur_mat))]) < 0.0001 &
                             rowSums(cur_mat[,grepl("Th17-_old", 
                                    colnames(cur_mat))]) < 0.0001 &
                             rowSums(cur_mat[,grepl("Th17-_young", 
                                    colnames(cur_mat))]) < 0.0001,]
cur_mat.old.Th1 <- cur_mat.old.Th1[order(rowMeans(cur_mat.old.Th1), 
                                         decreasing = TRUE),]

# Find Th17 young specific clones
cur_mat.young.Th17 <- cur_mat[rowSums(cur_mat[,grepl("Th17-_old", 
                              colnames(cur_mat))]) < 0.0001 &
                                rowSums(cur_mat[,grepl("Th1-_young", 
                              colnames(cur_mat))]) < 0.0001 & 
                                rowSums(cur_mat[,grepl("Th1-_old", 
                              colnames(cur_mat))]) < 0.0001,]
cur_mat.young.Th17 <- cur_mat.young.Th17[order(rowMeans(cur_mat.young.Th17),
                                             decreasing = TRUE),]

# Find Th17 old specific clones
cur_mat.old.Th17 <- cur_mat[rowSums(cur_mat[,grepl("Th17-_young",
                                    colnames(cur_mat))]) < 0.0001 & 
                              rowSums(cur_mat[,grepl("Th1-_old", 
                                    colnames(cur_mat))]) < 0.0001 &
                              rowSums(cur_mat[,grepl("Th1-_young",
                                    colnames(cur_mat))]) < 0.0001,]
cur_mat.old.Th17 <- cur_mat.old.Th17[order(rowMeans(cur_mat.old.Th17), 
                                         decreasing = TRUE),]

# Find Th17  specific clones
cur_mat.Th17 <- cur_mat[rowSums(cur_mat[,grepl("Th17-_young", 
                              colnames(cur_mat))]) > 0.0001 &
                          rowSums(cur_mat[,grepl("Th17-_old", 
                              colnames(cur_mat))]) > 0.0001 &
                          rowSums(cur_mat[,grepl("Th1-_young", 
                              colnames(cur_mat))]) < 0.0001 &
                          rowSums(cur_mat[,grepl("Th1-_young", 
                              colnames(cur_mat))]) < 0.0001,]
cur_mat.Th17 <- cur_mat.Th17[order(rowMeans(cur_mat.Th17),
                                             decreasing = TRUE),]

# Find Th1  specific clones
cur_mat.Th1 <- cur_mat[rowSums(cur_mat[,grepl("Th1-_young", 
                              colnames(cur_mat))]) > 0.0001 &
                          rowSums(cur_mat[,grepl("Th1-_old", 
                              colnames(cur_mat))]) > 0.0001 &
                          rowSums(cur_mat[,grepl("Th17-_young", 
                              colnames(cur_mat))]) < 0.0001 &
                          rowSums(cur_mat[,grepl("Th17-_old", 
                              colnames(cur_mat))]) < 0.0001,]
cur_mat.Th1 <- cur_mat.Th1[order(rowMeans(cur_mat.Th1),
                                             decreasing = TRUE),]

# Find shared clones
cur_mat.shared <- cur_mat[!(rownames(cur_mat) %in% 
                               c(rownames(cur_mat.old.Th1),
                                 rownames(cur_mat.young.Th1),
                                 rownames(cur_mat.old.Th17),
                                 rownames(cur_mat.young.Th17),
                                 rownames(cur_mat.Th1),
                                 rownames(cur_mat.Th17))),]
cur_mat.shared <- cur_mat.shared[order(rowMeans(cur_mat.shared), 
                                       decreasing = TRUE),]

# Visualize in form of heatmap
pdf("/Users/nils/Dropbox (Cambridge University)/GammaDelta/Analysis/Figures/Vg4_TRD_CDR3.pdf", 
    onefile = FALSE, width = 10, height = 25)
print(pheatmap(rbind(cur_mat.young.Th1, cur_mat.old.Th1, cur_mat.Th1,
               cur_mat.shared, cur_mat.Th17, cur_mat.young.Th17,
               cur_mat.old.Th17), 
         color = c("grey", colorRampPalette(c("white", "blue", "red"))(9999)),
         cluster_cols = FALSE, cluster_rows = FALSE, 
         breaks = seq(0, max(cur_mat), length.out = 10000), cellheight = 8, 
         fontsize = 7, gaps_row = c(44, 78, 87, 98, 113, 147),
         annotation_row = annot.df))
dev.off()
```

### Visualize clone fractions for each chain

```{r, fig.height=15, fig.width=15}
for(i in as.character(unique(annot.df$chain))){
  if(sum(annot.df$chain == i) < 2){next}
  cur_chain <- cur_mat[rownames(annot.df)[annot.df$chain == i],]
  cur_chain.melt <- melt(cur_chain)
  cur_chain.melt$Age <- sapply(as.character(cur_chain.melt$Var2), function(n){
    unlist(strsplit(n, "_"))[3]
  })
  cur_chain.melt$Priming <- sapply(as.character(cur_chain.melt$Var2), function(n){
    unlist(strsplit(n, "_"))[2]
  })
  cur_chain.melt <- cur_chain.melt[cur_chain.melt$Priming == "Th17-",]
  
  cur_p <- ggplot(cur_chain.melt, aes(Var1, value, fill = Age, group = Age)) + 
  geom_point(shape = 21, size = 3, position=position_dodge(width = 0.5)) + 
  theme(axis.title = element_text(size = 12), 
        axis.text.x = element_text(angle = 90, hjust = 1, size = 12)) + 
  xlab("Clone") + ylab("Clone fraction") + ggtitle(paste("Th17", i)) +
  scale_fill_manual(values = c("red", "white"))
  print(cur_p)
}
```

## Visuailze Vg6 cells

```{r}
# Merge clones
cur_clones <- data.frame(na = unique(c(Vg6_old_TRD$na, Vg6_young_TRD$na)),
                         aa = c(Vg6_old_TRD$aa, Vg6_young_TRD$aa)[
                           match(unique(c(Vg6_old_TRD$na, Vg6_young_TRD$na)),
                                 c(Vg6_old_TRD$na, Vg6_young_TRD$na))
                         ],
                         chain = c(Vg6_old_TRD$chain, Vg6_young_TRD$chain)[
                           match(unique(c(Vg6_old_TRD$na, Vg6_young_TRD$na)),
                                 c(Vg6_old_TRD$na, Vg6_young_TRD$na))
                         ])
rownames(cur_clones) <- cur_clones$na

c.names <- c(paste("Vg6_Th17-_young_TRD_X", 
                   1:sum(grepl("Vg6_Th17-young", TRG.files)), 
                   sep =  "_"), 
                   paste("Vg6_Th17-_old_TRD_X", 
                   1:sum(grepl("Vg6_Th17-old", TRG.files)), 
                   sep =  "_"))
cur_mat <- matrix(data = NA, ncol = length(c.names), 
              nrow = nrow(cur_clones))
colnames(cur_mat) <- c.names
rownames(cur_mat) <- cur_clones$na

for(i in c.names){
  cur_mat[,i] <- clones.fraction(all.files, i, cur_clones$na)
}
cur_mat <- cur_mat[order(rowMeans(cur_mat), decreasing = TRUE),]
rownames(cur_mat) <- paste(cur_clones[rownames(cur_mat),"na"],
                           cur_clones[rownames(cur_mat),"aa"], sep = ", ")

# Generate annotation data.frame
annot.df <- data.frame(row.names = rownames(cur_mat),
                       chain = cur_clones[sub(", [A-Z]*$", "", 
                                              rownames(cur_mat)),
                                          "chain"])

# Find old specific clones
cur_mat.old <- cur_mat[rowSums(cur_mat[,grepl("young", colnames(cur_mat))]) < 0.0001,]
cur_mat.old <- cur_mat.old[order(rowMeans(cur_mat.old), decreasing = TRUE),]

# Find young specific clones
cur_mat.young <- cur_mat[rowSums(cur_mat[,grepl("old", colnames(cur_mat))]) < 0.0001,]
cur_mat.young <- cur_mat.young[order(rowMeans(cur_mat.young), decreasing = TRUE),]

# Find shared clones
cur_mat.shared <- cur_mat[!(rownames(cur_mat) %in% 
                               c(rownames(cur_mat.old),
                                 rownames(cur_mat.young))),]


# Visualize in form of heatmap
pdf("/Users/nils/Dropbox (Cambridge University)/GammaDelta/Analysis/Figures/Vg6_TRD_CDR3.pdf", 
    onefile = FALSE, width = 10, height = 15)
print(pheatmap(rbind(cur_mat.old, cur_mat.shared, cur_mat.young), 
         color = c("grey", colorRampPalette(c("white", "blue", "red"))(9999)),
         cluster_cols = FALSE, cluster_rows = FALSE, 
         breaks = seq(0, max(cur_mat), length.out = 10000), cellheight = 8, 
         fontsize = 7, gaps_row = c(nrow(cur_mat.old), nrow(cur_mat.old)+nrow(cur_mat.shared)),
         annotation_row = annot.df))
dev.off()
```

