---
title: "Quanilty control based on clone detection"
author: "Nils Eling"
output: 
  html_document:
    toc: true
    toc_depth: 2
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, 
        encoding = encoding, output_file = '/Users/nils/Dropbox (Cambridge University)/GammaDelta/Analysis/Clones/ClonesQC.html') })
---

```{r}
knitr::opts_chunk$set(echo = TRUE)
```

This script visualizes the detection of gamma chanins in cell populations.
Due to sorting cells based on their gamma chain, contaminations can be easily detected.

# Gamma chain usage

## Read in data

```{r}
library(plyr)
library(reshape2)
library(ggplot2)
library(cowplot)

# Read in mixcr mapping results - one chain per .txt file
all.files <- list.files("/Users/nils/Dropbox (Cambridge University)/GammaDelta/Analysis/Clones/Txt_files", full.names = TRUE)

# Read in normalized counts
norm <- read.table("/Users/nils/Dropbox (Cambridge University)/GammaDelta/Analysis/Data/NormCounts.txt", sep = "\t", header = TRUE)
libraries <- sapply(colnames(norm), function(n){unlist(strsplit(n, "_"))[4]})

# Remove low quality libraries
all.files <- grep(paste(libraries,collapse="|"), all.files, value=TRUE, ignore.case = TRUE)

```

## Young V gamma 1 cells

```{r}
# Select gamma chain file for young V gamma 1 cells
Vg1.y <- lapply(as.list(all.files), function(n){
  if(grepl("Vg1" , n) & grepl("young" , n) & grepl("TRG" , n)){
    read.table(n, sep = "\t", header = TRUE, stringsAsFactors = FALSE)
  }
})
# Remove empty slots
Vg1.y <- Vg1.y[!unlist(lapply(Vg1.y, is.null))]

# Collect the clone fractions for variable clones
Vg1.y <- lapply(Vg1.y, function(n){
  n <- data.frame(n[,c("cloneFraction", "allVHitsWithScore")])
  n$allVHitsWithScore <- as.factor(as.character(sapply(n$allVHitsWithScore, function(x){unlist(strsplit(x, "\\*"))[1]})))
  n
})

# Sum across clone faction
sum.list <- lapply(Vg1.y, function(n){ddply(n, "allVHitsWithScore", summarise, sum = sum(cloneFraction))})

# Merge into one dataframe
mat <- matrix(data = NA, ncol = length(Vg1.y), 
              nrow = length(unique(unlist(sapply(sum.list, function(n){n$allVHitsWithScore})))))
rownames(mat) <- as.character(unique(unlist(sapply(sum.list, function(n){n$allVHitsWithScore}))))

for(i in 1:ncol(mat)){
  cur_n <- sum.list[[i]]
  mat[as.character(cur_n$allVHitsWithScore),i] <- cur_n$sum
}
mat[is.na(mat)] <- 0

# Plot results
df.melt <- melt(as.data.frame(t(mat)))

Vg1.y.p <- ggplot(df.melt, aes(variable, value)) + geom_point() + 
  theme(axis.title = element_text(size = 12), 
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  xlab("Gamma chain") + ylab("Chain fraction") + ggtitle("Vg1 young gamma chain usage")
Vg1.y.p
```

## Old V gamma 1 cells

```{r}
# Select gamma chain file for young V gamma 1 cells
Vg1.o <- lapply(as.list(all.files), function(n){
  if(grepl("Vg1" , n) & grepl("old" , n) & grepl("TRG" , n)){
    read.table(n, sep = "\t", header = TRUE, stringsAsFactors = FALSE)
  }
})
# Remove empty slots
Vg1.o <- Vg1.o[!unlist(lapply(Vg1.o, is.null))]

# Collect the clone fractions for variable clones
Vg1.o <- lapply(Vg1.o, function(n){
  n <- data.frame(n[,c("cloneFraction", "allVHitsWithScore")])
  n$allVHitsWithScore <- as.factor(as.character(sapply(n$allVHitsWithScore, function(x){unlist(strsplit(x, "\\*"))[1]})))
  n
})

# Sum across clone faction
sum.list <- lapply(Vg1.o, function(n){ddply(n, "allVHitsWithScore", summarise, sum = sum(cloneFraction))})

# Merge into one dataframe
mat <- matrix(data = NA, ncol = length(Vg1.o), 
              nrow = length(unique(unlist(sapply(sum.list, function(n){n$allVHitsWithScore})))))
rownames(mat) <- as.character(unique(unlist(sapply(sum.list, function(n){n$allVHitsWithScore}))))

for(i in 1:ncol(mat)){
  cur_n <- sum.list[[i]]
  mat[as.character(cur_n$allVHitsWithScore),i] <- cur_n$sum
}
mat[is.na(mat)] <- 0

# Plot results
df.melt <- melt(as.data.frame(t(mat)))

Vg1.o.p <- ggplot(df.melt, aes(variable, value)) + geom_point() + 
  theme(axis.title = element_text(size = 12), 
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  xlab("Gamma chain") + ylab("Chain fraction") + ggtitle("Vg1 old gamma chain usage")
Vg1.o.p
```

## Young V gamma 4 cells Th1 primed

```{r}
# Select gamma chain file for young V gamma 1 cells
Vg4.y.Th1 <- lapply(as.list(all.files), function(n){
  if(grepl("Vg4" , n) & grepl("young" , n) & grepl("TRG" , n) & !grepl("Th17" , n)){
    read.table(n, sep = "\t", header = TRUE, stringsAsFactors = FALSE)
  }
})
# Remove empty slots
Vg4.y.Th1 <- Vg4.y.Th1[!unlist(lapply(Vg4.y.Th1, is.null))]

# Collect the clone fractions for variable clones
Vg4.y.Th1 <- lapply(Vg4.y.Th1, function(n){
  n <- data.frame(n[,c("cloneFraction", "allVHitsWithScore")])
  n$allVHitsWithScore <- as.factor(as.character(sapply(n$allVHitsWithScore, function(x){unlist(strsplit(x, "\\*"))[1]})))
  n
})

# Sum across clone faction
sum.list <- lapply(Vg4.y.Th1, function(n){ddply(n, "allVHitsWithScore", summarise, sum = sum(cloneFraction))})

# Merge into one dataframe
mat <- matrix(data = NA, ncol = length(Vg4.y.Th1), 
              nrow = length(unique(unlist(sapply(sum.list, function(n){n$allVHitsWithScore})))))
rownames(mat) <- as.character(unique(unlist(sapply(sum.list, function(n){n$allVHitsWithScore}))))

for(i in 1:ncol(mat)){
  cur_n <- sum.list[[i]]
  mat[as.character(cur_n$allVHitsWithScore),i] <- cur_n$sum
}
mat[is.na(mat)] <- 0

# Plot results
df.melt <- melt(as.data.frame(t(mat)))

Vg4.y.Th1.p <- ggplot(df.melt, aes(variable, value)) + geom_point() + 
  theme(axis.title = element_text(size = 12), 
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  xlab("Gamma chain") + ylab("Chain fraction") + ggtitle("Vg4 Th1 young gamma chain usage")
Vg4.y.Th1.p
```

## Old V gamma 4 cells Th1 primed

```{r}
# Select gamma chain file for young V gamma 1 cells
Vg4.o.Th1 <- lapply(as.list(all.files), function(n){
  if(grepl("Vg4" , n) & grepl("old" , n) & grepl("TRG" , n) & !grepl("Th17" , n)){
    read.table(n, sep = "\t", header = TRUE, stringsAsFactors = FALSE)
  }
})
# Remove empty slots
Vg4.o.Th1 <- Vg4.o.Th1[!unlist(lapply(Vg4.o.Th1, is.null))]

# Collect the clone fractions for variable clones
Vg4.o.Th1 <- lapply(Vg4.o.Th1, function(n){
  n <- data.frame(n[,c("cloneFraction", "allVHitsWithScore")])
  n$allVHitsWithScore <- as.factor(as.character(sapply(n$allVHitsWithScore, function(x){unlist(strsplit(x, "\\*"))[1]})))
  n
})

# Sum across clone faction
sum.list <- lapply(Vg4.o.Th1, function(n){ddply(n, "allVHitsWithScore", summarise, sum = sum(cloneFraction))})

# Merge into one dataframe
mat <- matrix(data = NA, ncol = length(Vg4.o.Th1), 
              nrow = length(unique(unlist(sapply(sum.list, function(n){n$allVHitsWithScore})))))
rownames(mat) <- as.character(unique(unlist(sapply(sum.list, function(n){n$allVHitsWithScore}))))

for(i in 1:ncol(mat)){
  cur_n <- sum.list[[i]]
  mat[as.character(cur_n$allVHitsWithScore),i] <- cur_n$sum
}
mat[is.na(mat)] <- 0

# Plot results
df.melt <- melt(as.data.frame(t(mat)))

Vg4.o.Th1.p <- ggplot(df.melt, aes(variable, value)) + geom_point() + 
  theme(axis.title = element_text(size = 12), 
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  xlab("Gamma chain") + ylab("Chain fraction") + ggtitle("Vg4 Th1 old gamma chain usage")
Vg4.o.Th1.p
```

## Young V gamma 4 cells Th17 primed

```{r}
# Select gamma chain file for young V gamma 1 cells
Vg4.y.Th17 <- lapply(as.list(all.files), function(n){
  if(grepl("Vg4" , n) & grepl("young" , n) & grepl("TRG" , n) & grepl("Th17" , n)){
    read.table(n, sep = "\t", header = TRUE, stringsAsFactors = FALSE)
  }
})
# Remove empty slots
Vg4.y.Th17 <- Vg4.y.Th17[!unlist(lapply(Vg4.y.Th17, is.null))]

# Collect the clone fractions for variable clones
Vg4.y.Th17 <- lapply(Vg4.y.Th17, function(n){
  n <- data.frame(n[,c("cloneFraction", "allVHitsWithScore")])
  n$allVHitsWithScore <- as.factor(as.character(sapply(n$allVHitsWithScore, function(x){unlist(strsplit(x, "\\*"))[1]})))
  n
})

# Sum across clone faction
sum.list <- lapply(Vg4.y.Th17, function(n){ddply(n, "allVHitsWithScore", summarise, sum = sum(cloneFraction))})

# Merge into one dataframe
mat <- matrix(data = NA, ncol = length(Vg4.y.Th17), 
              nrow = length(unique(unlist(sapply(sum.list, function(n){n$allVHitsWithScore})))))
rownames(mat) <- as.character(unique(unlist(sapply(sum.list, function(n){n$allVHitsWithScore}))))

for(i in 1:ncol(mat)){
  cur_n <- sum.list[[i]]
  mat[as.character(cur_n$allVHitsWithScore),i] <- cur_n$sum
}
mat[is.na(mat)] <- 0

# Plot results
df.melt <- melt(as.data.frame(t(mat)))

Vg4.y.Th17.p <- ggplot(df.melt, aes(variable, value)) + geom_point() + 
  theme(axis.title = element_text(size = 12), 
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  xlab("Gamma chain") + ylab("Chain fraction") + ggtitle("Vg4 Th17 young gamma chain usage")
Vg4.y.Th17.p
```

## Old V gamma 4 cells Th17 primed

```{r}
# Select gamma chain file for young V gamma 1 cells
Vg4.o.Th17 <- lapply(as.list(all.files), function(n){
  if(grepl("Vg4" , n) & grepl("old" , n) & grepl("TRG" , n) & grepl("Th17" , n)){
    read.table(n, sep = "\t", header = TRUE, stringsAsFactors = FALSE)
  }
})
# Remove empty slots
Vg4.o.Th17 <- Vg4.o.Th17[!unlist(lapply(Vg4.o.Th17, is.null))]

# Collect the clone fractions for variable clones
Vg4.o.Th17 <- lapply(Vg4.o.Th17, function(n){
  n <- data.frame(n[,c("cloneFraction", "allVHitsWithScore")])
  n$allVHitsWithScore <- as.factor(as.character(sapply(n$allVHitsWithScore, function(x){unlist(strsplit(x, "\\*"))[1]})))
  n
})

# Sum across clone faction
sum.list <- lapply(Vg4.o.Th17, function(n){ddply(n, "allVHitsWithScore", summarise, sum = sum(cloneFraction))})

# Merge into one dataframe
mat <- matrix(data = NA, ncol = length(Vg4.o.Th17), 
              nrow = length(unique(unlist(sapply(sum.list, function(n){n$allVHitsWithScore})))))
rownames(mat) <- as.character(unique(unlist(sapply(sum.list, function(n){n$allVHitsWithScore}))))

for(i in 1:ncol(mat)){
  cur_n <- sum.list[[i]]
  mat[as.character(cur_n$allVHitsWithScore),i] <- cur_n$sum
}
mat[is.na(mat)] <- 0

# Plot results
df.melt <- melt(as.data.frame(t(mat)))

Vg4.o.Th17.p <- ggplot(df.melt, aes(variable, value)) + geom_point() + 
  theme(axis.title = element_text(size = 12), 
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  xlab("Gamma chain") + ylab("Chain fraction") + ggtitle("Vg4 Th17 old gamma chain usage")
Vg4.o.Th17.p
```

## Young V gamma 6 cells

```{r}
# Select gamma chain file for young V gamma 1 cells
Vg6.y <- lapply(as.list(all.files), function(n){
  if(grepl("Vg6" , n) & grepl("young" , n) & grepl("TRG" , n)){
    read.table(n, sep = "\t", header = TRUE, stringsAsFactors = FALSE)
  }
})
# Remove empty slots
Vg6.y <- Vg6.y[!unlist(lapply(Vg6.y, is.null))]

# Collect the clone fractions for variable clones
Vg6.y <- lapply(Vg6.y, function(n){
  n <- data.frame(n[,c("cloneFraction", "allVHitsWithScore")])
  n$allVHitsWithScore <- as.factor(as.character(sapply(n$allVHitsWithScore, function(x){unlist(strsplit(x, "\\*"))[1]})))
  n
})

# Sum across clone faction
sum.list <- lapply(Vg6.y, function(n){ddply(n, "allVHitsWithScore", summarise, sum = sum(cloneFraction))})

# Merge into one dataframe
mat <- matrix(data = NA, ncol = length(Vg6.y), 
              nrow = length(unique(unlist(sapply(sum.list, function(n){n$allVHitsWithScore})))))
rownames(mat) <- as.character(unique(unlist(sapply(sum.list, function(n){n$allVHitsWithScore}))))

for(i in 1:ncol(mat)){
  cur_n <- sum.list[[i]]
  mat[as.character(cur_n$allVHitsWithScore),i] <- cur_n$sum
}
mat[is.na(mat)] <- 0

# Plot results
df.melt <- melt(as.data.frame(t(mat)))

Vg6.y.p <- ggplot(df.melt, aes(variable, value)) + geom_point() + 
  theme(axis.title = element_text(size = 12), 
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  xlab("Gamma chain") + ylab("Chain fraction") + ggtitle("Vg6 young gamma chain usage")
Vg6.y.p
```

## Old V gamma 6 cells

```{r}
# Select gamma chain file for young V gamma 1 cells
Vg6.o <- lapply(as.list(all.files), function(n){
  if(grepl("Vg6" , n) & grepl("old" , n) & grepl("TRG" , n)){
    read.table(n, sep = "\t", header = TRUE, stringsAsFactors = FALSE)
  }
})
# Remove empty slots
Vg6.o <- Vg6.o[!unlist(lapply(Vg6.o, is.null))]

# Collect the clone fractions for variable clones
Vg6.o <- lapply(Vg6.o, function(n){
  n <- data.frame(n[,c("cloneFraction", "allVHitsWithScore")])
  n$allVHitsWithScore <- as.factor(as.character(sapply(n$allVHitsWithScore, function(x){unlist(strsplit(x, "\\*"))[1]})))
  n
})

# Sum across clone faction
sum.list <- lapply(Vg6.o, function(n){ddply(n, "allVHitsWithScore", summarise, sum = sum(cloneFraction))})

# Merge into one dataframe
mat <- matrix(data = NA, ncol = length(Vg6.o), 
              nrow = length(unique(unlist(sapply(sum.list, function(n){n$allVHitsWithScore})))))
rownames(mat) <- as.character(unique(unlist(sapply(sum.list, function(n){n$allVHitsWithScore}))))

for(i in 1:ncol(mat)){
  cur_n <- sum.list[[i]]
  mat[as.character(cur_n$allVHitsWithScore),i] <- cur_n$sum
}
mat[is.na(mat)] <- 0

# Plot results
df.melt <- melt(as.data.frame(t(mat)))

Vg6.o.p <- ggplot(df.melt, aes(variable, value)) + geom_point() + 
  theme(axis.title = element_text(size = 12), 
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  xlab("Gamma chain") + ylab("Chain fraction") + ggtitle("Vg6 old gamma chain usage")
Vg6.o.p
```

Save final figure

```{r}
final <- plot_grid(Vg1.y.p, Vg1.o.p,
                   Vg4.y.Th1.p, Vg4.o.Th1.p,
                   Vg4.y.Th17.p, Vg4.o.Th17.p,
                   Vg6.y.p, Vg6.o.p, ncol = 2, nrow = 4, align = "hv",
                   labels = "Auto")
ggsave("/Users/nils/Dropbox (Cambridge University)/GammaDelta/Analysis/Figures/GammaChainUsage_qualityControl.pdf", 
       final, width = 12, height = 15)
```

# Compare CDR3 sequences of Vg1 and Vg3 in Vg1 populations

## Vg1 young

```{r}
# Select gamma chain file for young V gamma 1 cells
Vg1.y <- lapply(as.list(all.files), function(n){
  if(grepl("Vg1" , n) & grepl("young" , n) & grepl("TRG" , n)){
    read.table(n, sep = "\t", header = TRUE, stringsAsFactors = FALSE)
  }
})
# Remove empty slots
Vg1.y <- Vg1.y[!unlist(lapply(Vg1.y, is.null))]

# Collect the clone fractions for variable clones
Vg1.y <- lapply(Vg1.y, function(n){
  n <- data.frame(n[,c("cloneFraction", "allVHitsWithScore", "clonalSequence")])
  n$allVHitsWithScore <- as.factor(as.character(sapply(n$allVHitsWithScore, function(x){unlist(strsplit(x, "\\*"))[1]})))
  n
})

# Shorten the CDR3 sequence to the first 10 nt
Vg1.y <- lapply(Vg1.y, function(n){
  n$clonalSequence <-  sapply(n$clonalSequence, function(x){paste(unlist(strsplit(x, ""))[1:10], collapse = "")})
  n
})

# Sum across similar sequences
Vg1.y <- lapply(Vg1.y, function(n){ddply(n, c("allVHitsWithScore", "clonalSequence"), summarise, sum = sum(cloneFraction))})

# Collect Clone fractions for Vg1 and Vg3 chains
Vg1.y.mat <- lapply(Vg1.y, function(n){
  cur_mat <- matrix(0, ncol = 2, nrow = length(unique(n$clonalSequence)))
  colnames(cur_mat) <- c("Vg1", "Vg3")
  rownames(cur_mat) <- unique(n$clonalSequence)
  cur_mat[n$clonalSequence[n$allVHitsWithScore ==  "TCRG-V1"],1] <-
    n$sum[n$allVHitsWithScore ==  "TCRG-V1"]
  cur_mat[n$clonalSequence[n$allVHitsWithScore ==  "TCRG-V3"],2] <-
    n$sum[n$allVHitsWithScore ==  "TCRG-V3"]
  cur_mat
})

# Combine results in one dataframe
df <- data.frame(clones = c(rownames(Vg1.y.mat[[1]]), rownames(Vg1.y.mat[[2]]),
                            rownames(Vg1.y.mat[[3]]), rownames(Vg1.y.mat[[4]]),
                            rownames(Vg1.y.mat[[5]]), rownames(Vg1.y.mat[[6]])),
                 Vg1 = c(Vg1.y.mat[[1]][,1], Vg1.y.mat[[2]][,1],
                         Vg1.y.mat[[3]][,1], Vg1.y.mat[[4]][,1],
                         Vg1.y.mat[[5]][,1], Vg1.y.mat[[6]][,1]),
                 Vg3 = c(Vg1.y.mat[[1]][,2], Vg1.y.mat[[2]][,2],
                         Vg1.y.mat[[3]][,2], Vg1.y.mat[[4]][,2],
                         Vg1.y.mat[[5]][,2], Vg1.y.mat[[6]][,2]),
                 Replicate = factor(c(rep(1, nrow(Vg1.y.mat[[1]])), rep(2, nrow(Vg1.y.mat[[2]])),
                               rep(3, nrow(Vg1.y.mat[[3]])), rep(4, nrow(Vg1.y.mat[[4]])),
                               rep(5, nrow(Vg1.y.mat[[5]])), rep(6, nrow(Vg1.y.mat[[6]])))))

# Plot results
Vg1.y.clones <- ggplot(df) + geom_point(aes(Vg1, Vg3)) + facet_grid(.~Replicate) + ggtitle("Vg1 young") + theme_bw() + theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_blank(),
        panel.border = element_rect(colour = "black"))
Vg1.y.clones
```

## Vg1 old

```{r}
# Select gamma chain file for young V gamma 1 cells
Vg1.o <- lapply(as.list(all.files), function(n){
  if(grepl("Vg1" , n) & grepl("old" , n) & grepl("TRG" , n)){
    read.table(n, sep = "\t", header = TRUE, stringsAsFactors = FALSE)
  }
})
# Remove empty slots
Vg1.o <- Vg1.o[!unlist(lapply(Vg1.o, is.null))]

# Collect the clone fractions for variable clones
Vg1.o <- lapply(Vg1.o, function(n){
  n <- data.frame(n[,c("cloneFraction", "allVHitsWithScore", "clonalSequence")])
  n$allVHitsWithScore <- as.factor(as.character(sapply(n$allVHitsWithScore, function(x){unlist(strsplit(x, "\\*"))[1]})))
  n
})

# Shorten the CDR3 sequence to the first 10 nt
Vg1.o <- lapply(Vg1.o, function(n){
  n$clonalSequence <-  sapply(n$clonalSequence, function(x){paste(unlist(strsplit(x, ""))[1:10], collapse = "")})
  n
})

# Sum across similar sequences
Vg1.o <- lapply(Vg1.o, function(n){ddply(n, c("allVHitsWithScore", "clonalSequence"), summarise, sum = sum(cloneFraction))})

# Collect Clone fractions for Vg1 and Vg3 chains
Vg1.o.mat <- lapply(Vg1.o, function(n){
  cur_mat <- matrix(0, ncol = 2, nrow = length(unique(n$clonalSequence)))
  colnames(cur_mat) <- c("Vg1", "Vg3")
  rownames(cur_mat) <- unique(n$clonalSequence)
  cur_mat[n$clonalSequence[n$allVHitsWithScore ==  "TCRG-V1"],1] <-
    n$sum[n$allVHitsWithScore ==  "TCRG-V1"]
  cur_mat[n$clonalSequence[n$allVHitsWithScore ==  "TCRG-V3"],2] <-
    n$sum[n$allVHitsWithScore ==  "TCRG-V3"]
  cur_mat
})

# Combine results in one dataframe
df <- data.frame(clones = c(rownames(Vg1.o.mat[[1]]), rownames(Vg1.o.mat[[2]]),
                            rownames(Vg1.o.mat[[3]]), rownames(Vg1.o.mat[[4]]),
                            rownames(Vg1.o.mat[[5]])),
                 Vg1 = c(Vg1.o.mat[[1]][,1], Vg1.o.mat[[2]][,1],
                         Vg1.o.mat[[3]][,1], Vg1.o.mat[[4]][,1],
                         Vg1.o.mat[[5]][,1]),
                 Vg3 = c(Vg1.o.mat[[1]][,2], Vg1.o.mat[[2]][,2],
                         Vg1.o.mat[[3]][,2], Vg1.o.mat[[4]][,2],
                         Vg1.o.mat[[5]][,2]),
                 Replicate = factor(c(rep(1, nrow(Vg1.o.mat[[1]])), rep(2, nrow(Vg1.o.mat[[2]])),
                               rep(3, nrow(Vg1.o.mat[[3]])), rep(4, nrow(Vg1.o.mat[[4]])),
                               rep(5, nrow(Vg1.o.mat[[5]])))))

# Plot results
Vg1.o.clones <- ggplot(df) + geom_point(aes(Vg1, Vg3)) + facet_grid(.~Replicate) + ggtitle("Vg1 old") + theme_bw() + theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_blank(),
        panel.border = element_rect(colour = "black"))
Vg1.o.clones
```

Save Figure

```{r}
final <- plot_grid(Vg1.y.clones,
                   Vg1.o.clones, ncol = 1, nrow = 2)

ggsave("/Users/nils/Dropbox (Cambridge University)/GammaDelta/Analysis/Figures/Vg1_Vg3_CDR3overlap.pdf", 
       final, width = 12, height = 8)
```