---
title: "Clone diversity"
author: "Nils Eling"
output: 
  html_document:
    toc: true
    toc_depth: 2
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, 
        encoding = encoding, output_file = '/Users/nils/Dropbox (Cambridge University)/GammaDelta/Analysis/Clones/Clone_diversity.html') })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(plyr)
library(reshape2)
library(ggplot2)
library(cowplot)
library(pheatmap)
library(openxlsx)
source("../../Functions/auxiliary.R")

# Read in mixcr mapping results - one chain per .txt file
all.files <- list.files("/Users/nils/Dropbox (Cambridge University)/GammaDelta/Analysis/Clones/Txt_files", full.names = TRUE)

# Read in normalized counts
norm <- read.table("/Users/nils/Dropbox (Cambridge University)/GammaDelta/Analysis/Data/NormCounts.txt", sep = "\t", header = TRUE)
libraries <- sapply(colnames(norm), function(n){unlist(strsplit(n, "_"))[4]})

# Remove low quality libraries
all.files <- grep(paste(libraries,collapse="|"), all.files, value=TRUE, ignore.case = TRUE)

# All files containing TRG
TRG.files <- all.files[grepl("TRG", all.files)]
TRD.files <- all.files[grepl("TRD", all.files)]
```

# TRG analysis

## Vg4 Th1 cells

### For individual sequences

Each individual sequence is counted only once regardless of abundance

```{r}
cur_files <- TRG.files[grepl("Vg4_Th1-", TRG.files)]
cur_names <- paste(sub("_unk.*$", "", 
                 substring(TRG.files[grepl("Vg4_Th1-", TRG.files)], 106)), "-",
                 1:length(cur_files), sep = "")
cur_files <- cur_files[order(cur_names)]
cur_names <- cur_names[order(cur_names)]

Vg4.Th1 <- clone_diversity(cur_files, cur_names, select = "TCRG-V4")

# Plot results
Vg4.Th1.melt <- melt(Vg4.Th1)
Vg4.Th1.melt$Age <- factor(sapply(as.character(Vg4.Th1.melt$Var2),
                           function(n){unlist(strsplit(n, "-"))[2]}),
                           levels = c("old", "young"))
Vg4.Th1.melt$Replicate <- c(rep(1:4, each = 5), rep(1:6, each = 5))


ggplot(Vg4.Th1.melt) + 
  geom_bar(aes(Replicate, value, fill = factor(Var1)),
           stat = "identity") + 
  facet_grid(.~Age, scales = "free_x") + 
  scale_fill_manual(name = "Diversity", 
        values = c("dark blue", "blue", "steelblue", "dark green", "orange"))
```

### Considering the size of the clone

```{r}
cur_files <- TRG.files[grepl("Vg4_Th1-", TRG.files)]
cur_names <- paste(sub("_unk.*$", "", 
                 substring(TRG.files[grepl("Vg4_Th1-", TRG.files)], 106)), "-",
                 1:length(cur_files), sep = "")
cur_files <- cur_files[order(cur_names)]
cur_names <- cur_names[order(cur_names)]

Vg4.Th1 <- clone_diversity(cur_files, cur_names, select = "TCRG-V4",
                           all.reads = TRUE)

# Plot results
Vg4.Th1.melt <- melt(Vg4.Th1)
Vg4.Th1.melt$Age <- factor(sapply(as.character(Vg4.Th1.melt$Var2),
                           function(n){unlist(strsplit(n, "-"))[2]}),
                           levels = c("old", "young"))
Vg4.Th1.melt$Replicate <- c(rep(1:4, each = 5), rep(1:6, each = 5))


ggplot(Vg4.Th1.melt) + 
  geom_bar(aes(Replicate, value, fill = factor(Var1)),
           stat = "identity") + 
  facet_grid(.~Age, scales = "free_x") + 
  scale_fill_manual(name = "Diversity", 
        values = c("dark blue", "blue", "steelblue", "dark green", "orange"))
```

## Vg4 Th17 cells

### For individual sequences

Each individual sequence is counted only once regardless of abundance

```{r}
cur_files <- TRG.files[grepl("Vg4_Th17-", TRG.files)]
cur_names <- paste(sub("_unk.*$", "", 
                 substring(TRG.files[grepl("Vg4_Th17-", TRG.files)], 106)), "-",
                 1:length(cur_files), sep = "")
cur_files <- cur_files[order(cur_names)]
cur_names <- cur_names[order(cur_names)]

Vg4.Th17 <- clone_diversity(cur_files, cur_names, select = "TCRG-V4")

# Plot results
Vg4.Th17.melt <- melt(Vg4.Th17)
Vg4.Th17.melt$Age <- factor(sapply(as.character(Vg4.Th17.melt$Var2),
                           function(n){unlist(strsplit(n, "-"))[2]}),
                           levels = c("old", "young"))
Vg4.Th17.melt$Replicate <- c(rep(1:4, each = 5), rep(1:6, each = 5))


ggplot(Vg4.Th17.melt) + 
  geom_bar(aes(Replicate, value, fill = factor(Var1)),
           stat = "identity") + 
  facet_grid(.~Age, scales = "free_x") + 
  scale_fill_manual(name = "Diversity", 
        values = c("dark blue", "blue", "steelblue", "dark green", "orange"))
```

### Considering the size of the clone

```{r}
cur_files <- TRG.files[grepl("Vg4_Th17-", TRG.files)]
cur_names <- paste(sub("_unk.*$", "", 
                 substring(TRG.files[grepl("Vg4_Th17-", TRG.files)], 106)), "-",
                 1:length(cur_files), sep = "")
cur_files <- cur_files[order(cur_names)]
cur_names <- cur_names[order(cur_names)]

Vg4.Th17 <- clone_diversity(cur_files, cur_names, select = "TCRG-V4",
                           all.reads = TRUE)

# Plot results
Vg4.Th17.melt <- melt(Vg4.Th17)
Vg4.Th17.melt$Age <- factor(sapply(as.character(Vg4.Th17.melt$Var2),
                           function(n){unlist(strsplit(n, "-"))[2]}),
                           levels = c("old", "young"))
Vg4.Th17.melt$Replicate <- c(rep(1:4, each = 5), rep(1:6, each = 5))


ggplot(Vg4.Th17.melt) + 
  geom_bar(aes(Replicate, value, fill = factor(Var1)),
           stat = "identity") + 
  facet_grid(.~Age, scales = "free_x") + 
  scale_fill_manual(name = "Diversity", 
        values = c("dark blue", "blue", "steelblue", "dark green", "orange"))
```

# TRD analysis

## Vg4 Th1 cells

### For individual sequences

Each individual sequence is counted only once regardless of abundance

```{r}
cur_files <- TRD.files[grepl("Vg4_Th1-", TRD.files)]
cur_names <- paste(sub("_unk.*$", "", 
                 substring(TRD.files[grepl("Vg4_Th1-", TRD.files)], 106)), "-",
                 1:length(cur_files), sep = "")
cur_files <- cur_files[order(cur_names)]
cur_names <- cur_names[order(cur_names)]

Vg4.Th1 <- clone_diversity(cur_files, cur_names)

# Plot results
Vg4.Th1.melt <- melt(Vg4.Th1)
Vg4.Th1.melt$Age <- factor(sapply(as.character(Vg4.Th1.melt$Var2),
                           function(n){unlist(strsplit(n, "-"))[2]}),
                           levels = c("old", "young"))
Vg4.Th1.melt$Replicate <- c(rep(1:4, each = 5), rep(1:6, each = 5))


ggplot(Vg4.Th1.melt) + 
  geom_bar(aes(Replicate, value, fill = factor(Var1)),
           stat = "identity") + 
  facet_grid(.~Age, scales = "free_x") + 
  scale_fill_manual(name = "Diversity", 
        values = c("dark blue", "blue", "steelblue", "dark green", "orange"))
```

### Considering the size of the clone

```{r}
cur_files <- TRD.files[grepl("Vg4_Th1-", TRD.files)]
cur_names <- paste(sub("_unk.*$", "", 
                 substring(TRD.files[grepl("Vg4_Th1-", TRD.files)], 106)), "-",
                 1:length(cur_files), sep = "")
cur_files <- cur_files[order(cur_names)]
cur_names <- cur_names[order(cur_names)]

Vg4.Th1 <- clone_diversity(cur_files, cur_names,
                           all.reads = TRUE)

# Plot results
Vg4.Th1.melt <- melt(Vg4.Th1)
Vg4.Th1.melt$Age <- factor(sapply(as.character(Vg4.Th1.melt$Var2),
                           function(n){unlist(strsplit(n, "-"))[2]}),
                           levels = c("old", "young"))
Vg4.Th1.melt$Replicate <- c(rep(1:4, each = 5), rep(1:6, each = 5))


ggplot(Vg4.Th1.melt) + 
  geom_bar(aes(Replicate, value, fill = factor(Var1)),
           stat = "identity") + 
  facet_grid(.~Age, scales = "free_x") + 
  scale_fill_manual(name = "Diversity", 
        values = c("dark blue", "blue", "steelblue", "dark green", "orange"))
```

## Vg4 Th17 cells

### For individual sequences

Each individual sequence is counted only once regardless of abundance

```{r}
cur_files <- TRD.files[grepl("Vg4_Th17-", TRD.files)]
cur_names <- paste(sub("_unk.*$", "", 
                 substring(TRD.files[grepl("Vg4_Th17-", TRD.files)], 106)), "-",
                 1:length(cur_files), sep = "")
cur_files <- cur_files[order(cur_names)]
cur_names <- cur_names[order(cur_names)]

Vg4.Th17 <- clone_diversity(cur_files, cur_names)

# Plot results
Vg4.Th17.melt <- melt(Vg4.Th17)
Vg4.Th17.melt$Age <- factor(sapply(as.character(Vg4.Th17.melt$Var2),
                           function(n){unlist(strsplit(n, "-"))[2]}),
                           levels = c("old", "young"))
Vg4.Th17.melt$Replicate <- c(rep(1:4, each = 5), rep(1:6, each = 5))


ggplot(Vg4.Th17.melt) + 
  geom_bar(aes(Replicate, value, fill = factor(Var1)),
           stat = "identity") + 
  facet_grid(.~Age, scales = "free_x") + 
  scale_fill_manual(name = "Diversity", 
        values = c("dark blue", "blue", "steelblue", "dark green", "orange"))
```

### Considering the size of the clone

```{r}
cur_files <- TRD.files[grepl("Vg4_Th17-", TRD.files)]
cur_names <- paste(sub("_unk.*$", "", 
                 substring(TRD.files[grepl("Vg4_Th17-", TRD.files)], 106)), "-",
                 1:length(cur_files), sep = "")
cur_files <- cur_files[order(cur_names)]
cur_names <- cur_names[order(cur_names)]

Vg4.Th17 <- clone_diversity(cur_files, cur_names,
                           all.reads = TRUE)

# Plot results
Vg4.Th17.melt <- melt(Vg4.Th17)
Vg4.Th17.melt$Age <- factor(sapply(as.character(Vg4.Th17.melt$Var2),
                           function(n){unlist(strsplit(n, "-"))[2]}),
                           levels = c("old", "young"))
Vg4.Th17.melt$Replicate <- c(rep(1:4, each = 5), rep(1:6, each = 5))


ggplot(Vg4.Th17.melt) + 
  geom_bar(aes(Replicate, value, fill = factor(Var1)),
           stat = "identity") + 
  facet_grid(.~Age, scales = "free_x") + 
  scale_fill_manual(name = "Diversity", 
        values = c("dark blue", "blue", "steelblue", "dark green", "orange"))
```